---
title: "Analyzing Netflix data"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---





## Some of the interesting questions (tasks) which can be performed on this dataset -

- Understanding what content is available in different countries
- Identifying similar content by matching text-based features
- Network analysis of Actors / Directors and find interesting insights
- Is Netflix has increasingly focusing on TV rather than movies in recent years.
- What types of genres are more in demand over the years


### Lets Read the data and have a look at some basic things:

```{r message=FALSE,warning=FALSE}

#reading the data
netflixdf <- read.csv("netflix_titles.csv")
attach(netflixdf)

require(dplyr)
require(highcharter)
#let's see the distribution on type of shows on Netflix:
table(type)

#let's check summary statistics of the dataset
summary(netflixdf)

```




### Let's start with analyzing  the Genres on Netflix

How the Genre of shows on Neflix relates to the other interesting variables in the dataset like country of origin, year released, type and ratings.

```{r message=FALSE,warning=FALSE}

#let's check top Genre of shows in netflix:

Genre_df <- netflixdf %>%
  group_by(listed_in) %>% 
  summarise(Count = n()) %>% 
  arrange(desc(Count)) %>% 
  top_n(30)
   

#let's plot the most produced  genres:

hchart(Genre_df,hcaes(x=listed_in,y=Count),type="column",color="#062D67",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of top 30 genres produced on Netflix",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



```
Shockingly there are most __"documentaries"__ on Netflix followe by __"Stand up Comedy"__ shows.


Let's check what genres were released what year.


```{r  warning=FALSE,message=FALSE}


year_genref  <- netflixdf %>% 
  filter(listed_in %in% Genre_df$listed_in)  %>% 
  select(listed_in,release_year) %>% 
  group_by(release_year,listed_in) %>% 
  mutate(Count = n())  %>% 
  arrange(desc(Count)) %>% 
  arrange(desc(release_year))
  
  
#creating dataframes for all years

year_2019 <- year_genref %>% 
  filter(release_year == "2019") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

year_2020 <- year_genref %>% 
  filter(release_year == "2020") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

year_2018 <- year_genref %>% 
  filter(release_year == "2018") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

year_2017 <- year_genref %>% 
  filter(release_year == "2017") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

year_2016 <- year_genref %>% 
  filter(release_year == "2016") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

year_2015 <- year_genref %>% 
  filter(release_year == "2015") %>% 
  group_by(listed_in) %>% 
  summarise(nCount= n()) %>% 
  arrange(desc(nCount))

```


### Let's plot the above data for last 5 years.


#### For year 2019

```{r ,message=FALSE,warning=FALSE,echo=FALSE}

  hchart(year_2019,hcaes(x=listed_in,y=nCount),type="column",color="blue",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Year 2019",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 
  
```  
  
In 2019, most of the shows produced and released on Netflix were __Stand-Up comedy__ shows followed by __Documentaries__.  
  
#### For year 2018
  
```{r ,echo=FALSE,message=FALSE,warning=FALSE}

  hchart(year_2018,hcaes(x=listed_in,y=nCount),type="column",color="green",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Year 2018 ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 
  
  
```




#### For year 2017

```{r ,echo=FALSE,message=FALSE,warning=FALSE}

  hchart(year_2017,hcaes(x=listed_in,y=nCount),type="column",color="orange",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Year 2017 ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 
 
```




#### For year 2016

```{r ,echo=FALSE,message=FALSE,warning=FALSE}

  hchart(year_2016,hcaes(x=listed_in,y=nCount),type="column",color="purple",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Year 2016 ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 


```


#### For year 2015

```{r ,echo=FALSE,message=FALSE,warning=FALSE}

  hchart(year_2015,hcaes(x=listed_in,y=nCount),type="column",color="red",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Year 2015 ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 
  
```

We can actually notice the popularity and demand of __stand-up comedy__ shows growing in the past 5 years in the above plots.





### Let's check the relation between Country and the Top Genres


Here we will try to find which country produces which kinds of shows. First let's check which Country produces the most shows for Netflix.

```{r, message=FALSE,warning=FALSE}


top_country <- netflixdf %>% 
  select(country) %>% 
  group_by(country) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount)) %>% 
  top_n(20)

#setting missing column as NA
top_country[3,] <- NA
top_country <- na.omit(top_country)

top_country

```

So most of the shows are produced by following countries:
1) US
2) India
3) UK
4) Japan
5) Canada
6) South Korea



```{r  message=FALSE,warning=FALSE}

#now lets filter top countries and the top genres

country_df <- netflixdf %>% 
  filter(listed_in %in% Genre_df$listed_in  & country %in% top_country$country) %>% 
  select(listed_in,country) %>% 
  group_by(listed_in, country) %>% 
  mutate(nCount = n())


```






```{r message=FALSE,warning=FALSE}

US_shows <- country_df  %>% 
  filter(country=="United States") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))


India_shows <- country_df  %>% 
  filter(country=="India") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))



UK_shows <- country_df  %>% 
  filter(country=="United Kingdom") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))
  

Japan_shows <- country_df  %>% 
  filter(country=="Japan") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))


Canada_shows <- country_df  %>% 
  filter(country=="Canada") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))
  
  
SK_shows <- country_df  %>% 
  filter(country=="South Korea") %>% 
  group_by(listed_in) %>% 
  summarise(nCount = n()) %>% 
  arrange(desc(nCount))
  


```


### Let's plot the data for all top countries





#### 1)Types of shows in US 

```{r echo=FALSE,warning=FALSE,message=FALSE}

hchart(US_shows,hcaes(x=listed_in,y=nCount),type="column",color="#FF6666",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in US ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```



#### 2)Types of shows in India 

```{r echo=FALSE,warning=FALSE,message=FALSE}
hchart(India_shows,hcaes(x=listed_in,y=nCount),type="column",color="#6666FF",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in India ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```



#### 3)Types of shows in UK

```{r echo=FALSE,warning=FALSE,message=FALSE}

hchart(UK_shows,hcaes(x=listed_in,y=nCount),type="column",color="#FF66FF",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in UK ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```



#### 4)Types of shows Canada

```{r echo=FALSE,warning=FALSE,message=FALSE}

hchart(US_shows,hcaes(x=listed_in,y=nCount),type="column",color="#404040",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Canada",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```



#### 5)Types of shows in Japan

```{r echo=FALSE,warning=FALSE,message=FALSE}


hchart(Japan_shows,hcaes(x=listed_in,y=nCount),type="column",color="#CCE5FF",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in Japan ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 


```


#### 6)Types of shows in South Korea 

```{r echo=FALSE,warning=FALSE,message=FALSE}

hchart(SK_shows,hcaes(x=listed_in,y=nCount),type="column",color="#FFFF99",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Top Genres of shows produced in South Korea ",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```




------------------------



### Genre and Type of Show


Let's check which genres are which types of shows(Movies/TV Series).






